\renewcommand{\theequation}{\theenumi}
\renewcommand{\thefigure}{\theenumi}
\renewcommand{\thetable}{\theenumi}
\begin{enumerate}[label=\thesection.\arabic*.,ref=\thesection.\theenumi]
\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}
\numberwithin{table}{enumi}

\item Two independent random variables \(X\) and \(Y\)
are uniformly distributed in the interval [-1,1].The probability that max \{\(X\),\(Y\)\} is less than \(\frac{1}{2}\) is
\begin{enumerate}[label={\Alph*)}]
    \item 3/4
    \item 9/16
    \item 1/4
    \item 2/3
\end{enumerate}
\solution
\input{indep/solutions/1.tex}

\item Three fair cubical dice are thrown simultaneously. The probability that all three dice have the same number of dots on the faces showing up is (up to third decimal place)...........
\solution
\input{solutions/4.tex}
%
\item Given Set A = [2,3,4,5] and Set B = [11,12,13,14,15], two numbers are randomly selected,one from each set. What is probability that the sum of the two numbers equals 16?

\begin{enumerate}
\begin{multicols}{4}
\setlength\itemsep{2em}

\item $
0.20
$
\item $
0.25
$
\item $
0.30
$
\item $
0.33
$

\end{multicols}
\end{enumerate}
\solution
\input{solutions/7/7.tex}
%
\item Two independent random variables X and Y are uniformly distributed in the interval $[-1,1]$.The probability that max$[X,Y]$ is less than $\dfrac{1}{2}$ is

\begin{enumerate}
\begin{multicols}{4}
\setlength\itemsep{2em}

\item $
\dfrac{3}{4}
$
\item $
\dfrac{9}{16}
$
\item $
\dfrac{1}{4}
$
\item $
\dfrac{2}{3}
$
\end{multicols}
\end{enumerate}
%
\item A fair dice is tossed two times. The probability that the second toss result in a value that is higher than the first toss is
\begin{enumerate}
\begin{multicols}{4}
\setlength\itemsep{2em}
\item $
\dfrac{2}{36}
$
\item $
\dfrac{2}{6}
$
\item $
\dfrac{5}{12}
$
\item $
\dfrac{1}{2}
$
\end{multicols}
\end{enumerate}
%
\solution
\input{solutions/ec/26.tex}
%
\item Consider two independent random variables X and Y with identical distributions. The variables X and Y take value 0, 1 and 2 with probabilities $\dfrac{1}{2}$, $\dfrac{1}{4}$ and $\dfrac{1}{4}$ rrespectively. What is the conditional probability $P(X+Y = 2|X-Y =0)$?

\begin{enumerate}
\begin{multicols}{4}
\setlength\itemsep{2em}

\item 0
\item $\dfrac{1}{16}$
\item $\dfrac{1}{6}$
\item 1

\end{multicols}
\end{enumerate}
%
\solution
\input{solutions/ec/28.tex}
%
\item Let X and Y be two statistically independent random variables uniformly distributed in the range $(-1,1)$ and $(-2,1)$ respectively. Let $Z = X+Y$, then the probability that $[Z\leqslant-2]$ is
\begin{enumerate}
\begin{multicols}{4}
\setlength\itemsep{2em}
\item zero
\item $\dfrac{1}{6}$
\item $\dfrac{1}{3}$
\item $\dfrac{1}{12}$
\end{multicols}
\end{enumerate}
%
\solution
\input{solutions/ec/34/Assignment_3.tex}


%
\item Let $X_1$, $X_2$, $X_3$ and $X_4$ be independent normal random variables with zero mean and unit variance. The probability that $X_4$ is the smallest among the four is..... 
\\
\solution
\input{solutions/ec/2018.tex}

\item Let $A_{1},A_{2},.....A_{n}$ be n independent events in which the Probability of occurence of the event $A_{i}$ is given by P($A_{i}$) = 1 - $\frac{1}{\alpha^i}$, $\alpha >1$, i = 1,2,3,....n.Then the probability that atleast one of the events occurs is
\begin{enumerate}
    \item  1 - $\frac{1}{\alpha^\frac{n(n+1)}{2}}$ \hspace{0.95cm}
    \item  $\frac{1}{\alpha^\frac{n(n+1)}{2}}$\hspace{1.5cm}
    \\ \\
    \item  $\frac{1}{\alpha^n}$ \hspace{2.15cm}
    \item 1 - $\frac{1}{\alpha^n}$\hspace{0.95cm}
  \end{enumerate}
  %
  \solution
  \input{solutions/adv/ma/2005/25.tex}
  %
  \item Let $X_{1},X_{2},\dots$, be a sequence of independent and identically distributed random variables with $P(X_{1}=1)=\dfrac{1}{4}$ and $P(X_{1}=2)=\dfrac{3}{4}$. If $\bar X_{n}=\dfrac{1}{n}\displaystyle\sum_{i=1}^{n}X_{i}$,  for $n=1,2,\dots$, then $\displaystyle\lim_{n\to\infty}P(\bar X_{n} \leq 1.8)$ is equal to
  \\
  \solution
  \input{solutions/adv/ma/2015/32.tex}
  \item  Let $\{X_n\}_{n\ge 1}$ be a sequence of independent and identically distributed random variables each having uniform distribution on [0,3]. Let $Y$ be a random variable, independent of $\{X_n\}_{n\ge 1}$, having probability mass function
  \begin{align}
  \pr{Y=k} = 
  \begin{cases}
  \frac{1}{(e-1)k!} & k=1,2,3\cdots \\
  0 & otherwise
  \end{cases}
  \end{align}
  Then $\pr{max\{X_1,X_2,\cdots X_Y\}\le 1}$ equals ............\\
  %
  \solution
    \input{solutions/adv/st/2021/48.tex}
%
\item Let $X_1$, $X_2$ and $X_3$ be independent and identically distributed random variables with $E(X_1) = 0$ and $E\left(X^2_1\right)=\frac{15}{4}$. If $\psi : (0,\infty) \rightarrow (0,\infty)$ is defined through the conditional expectiation
$\psi(t) = E\left(X^2_1 | X_1^2 + X_2^2 + X_3^2 = t\right), t>0$
Then, $E(\psi((X_1+X_2)^2))$ is equal to,
%
\\
\solution
  \input{solutions/adv/ma/2015/28.tex}
%
\item Let $X \sim B\brak{5,\frac{1}{2}}$ and $Y \sim U(0,1)$. The the value of:
\[
    \frac{\pr{X+Y \leq 2}}{\pr{X+Y \geq 5}}
\]
is equal to? ($X$ and $Y$ are independent)
\solution 
  \input{solutions/adv/challenge/1.tex}

\item A die is thrown again and again until three sixes are obtained.Find the probability of obtaining the third six in the sixth row of a die.
\end{enumerate}