\renewcommand{\theequation}{\theenumi}
\renewcommand{\thefigure}{\theenumi}
\renewcommand{\thetable}{\theenumi}
\begin{enumerate}[label=\thesection.\arabic*.,ref=\thesection.\theenumi]
\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}
\numberwithin{table}{enumi}


\item Let U and V be two independent zero mean Gaussian random variables of variances $\dfrac{1}{4}$ and $\dfrac{1}{9}$ respectively. The probability $P(3V\geqslant2U)$ is
\begin{enumerate}
\begin{multicols}{4}
\setlength\itemsep{2em}
\item $
\dfrac{4}{9}
$
\item $
\dfrac{1}{2}
$
\item $
\dfrac{2}{3}
$
\item $
\dfrac{5}{9}
$
\end{multicols}
\end{enumerate}
%
\item Consider a binary digital communication system with equally likely 0's and 1's. When binary 0 is transmitted the voltage at the detector input can lie between the level -0.25V and +0.25V with equal probability: when binary 1 is transmitted, the voltage at the detector can have any value between 0 and 1V with equal probability. If the detector has a threshold of 2.0V (i.e., if the received signal is greater than 0.2V, the bit is taken as 1), the average bit error probability is
\begin{enumerate}
\begin{multicols}{4}
\setlength\itemsep{2em}

\item 0.15
\item 0.2
\item 0.05
\item 0.5
\end{multicols}
\end{enumerate}
%
\item Let X be the Gaussian random variable obtained by sampling the process at $t=t_i$ and let 
\begin{equation*}
Q(\alpha)={\int_{\alpha}^{\infty}}\dfrac{1}{\sqrt{2\pi}}e^{\frac{-y^2}{2}}dy
\end{equation*}
%
The probability that $[\textit{X}\leqslant1]$ is \dots
%
\item Let X be a zero mean unit variance Gaussian random variable. $E[|X|]$ is equal to .........
%
\\
\solution
\input{solutions/ec/42.tex}

\item Consider a discrete-time channel $Y = X+Z$, where the additive noise Z is signal-dependent. In particular, given the transmitted symbol $X \in \{-a,+a\}$ at any instant, the noise sample Z is chosen independently from a Gaussian distribution with mean $\beta X$ and unit variance. Assume a threshold detector with zero threshold at the receiver.\\
When $\beta = 0$, the BER was found to be $Q(a) = 1 \times {10^-8}$.\\
$$
\bigg(Q(v)= \dfrac{1}{\sqrt{2 \pi}} \int_{v}^{\infty} e^{\frac{-u^2}{2}}du$$, and for $v>1$, use $Q(v) \approx e^{\frac{-v^2}{2}} \bigg)$ \\
When $\beta = -0.3$, the BER is closet to

\begin{enumerate}
\begin{multicols}{2}
\setlength\itemsep{2em}

\item $10^-7$
\item $10^-6$
\item $10^-4$ \label{option C}
\item $10^-2$

\end{multicols}
\end{enumerate}
%
\solution
\input{solutions/ec/45/Assignment3.tex}
\item Suppose $X$ and $Y$ are two random variables such that $aX + bY$ is a normal random variable for all $a,b \in \mathbb{R}$. Consider the following statements P,Q,R and S:


 (P): $X$ is a standard normal random variable.\\
 (Q): The conditional distribution of $X$ given $Y$ is normal.\\
 (R): The conditional distribution of $X$ given $X$ + $Y$ is normal.\\
 (S): $X$ - $Y$ has mean $0$.\\

Which of the above statements ALWAYS hold TRUE?
\begin{enumerate}
\begin{multicols}{2}
\setlength\itemsep{2em}

\item both P and Q
\item both Q and R
\item both Q and S
\item both P and S

\end{multicols}
\end{enumerate}

\item A random variable $X$ takes values -1 and +1 with probabilities 0.2 and 0.8, respectively.
It is transmitted across a channel which adds noise $N$, so that the random variable at the
channel output is $Y = X + N$. The noise $N$ is independent of $X$, and is uniformly
distributed over the interval [-2 , 2]. The receiver makes a decision
\[
\hat{X} = \begin{cases}
            -1, &\text{if}\quad Y \leq \theta \\
             +1, &\text{if}\quad Y \geq \theta\\
            \end{cases}
\]
where the threshold $\theta  \in [-1,1]$ is chosen so as to minimize the probability of error
\pr {\hat{X} \neq X}. The minimum probability of error, rounded off to 1 decimal place, is \dots
\\
\solution
\input{solutions/ec/2019/47/Assignment2.tex}

%
\item  Let $U$ and $V$ be two independent zero mean Gaussian random variables of variances $\frac{1}{4}$ and $\frac{1}{9}$ respectively. The probability $\pr{3V\geq2U }$ is
\begin{enumerate}
    \item $4/9$
    \item $1/2$
    \item $2/3$
    \item $5/9$
\end{enumerate}
%
\solution
\input{solutions/ec/2013/26.tex}
%
%
\item Let X be a standard normal random variable. Then $\pr{X < 0 |\;\abs{\lfloor X\rfloor} = 1}$ is equal to
\begin{enumerate}[label = \alph*)]
    \item $\cfrac{\Phi(1) - \frac{1}{2}}{\Phi(2) - \frac{1}{2}}$
    \item $\cfrac{\Phi(1) + \frac{1}{2}}{\Phi(2) + \frac{1}{2}}$
    \item $\cfrac{\Phi(1) - \frac{1}{2}}{\Phi(2) + \frac{1}{2}}$
    \item $\cfrac{\Phi(1) + 1}{\Phi(2) + 1}$
\end{enumerate}
%
\solution
\input{solutions/adv/ma/2016/49.tex}
%
\item Let $(X,Y)$ have a bivariate normal distribution with the joint probability density function
\begin{align}
f_{X,Y}(x,y)=\frac{1}{\pi}e^{(\frac{3}{2}xy-\frac{25}{32}x^2-2y^2)}\\
-\infty < x,y < \infty
\end{align}
Then $E(XY)$ equals 
%
\\
\solution
  \input{solutions/adv/st/2021/44.tex}

  \item Let \(X_1,X_2\)... be a sequence of independent and identically distributed random variable with
  \begin{align}
      \pr{X_1=-1}=\pr{X_1=1}=1/2
  \end{align}
  Suppose for the standard normal random variable Z,
  \begin{align}
  &\pr{-0.1\leq Z \leq 0.1}=0.08 .\label{qneq} \\ \nonumber
  &\text{If } S_n= \sum_{i=1}^{n^2} X_i ,\text{then} \lim_{n\to\infty} \pr{S_n >\frac{n}{10}} =
  \end{align}
  \begin{enumerate}
      \item 0.42
      \item 0.46
      \item 0.50
      \item 0.54
  \end{enumerate}
  \solution
    \input{solutions/adv/ma/2007/55.tex}
%
\item Robot Ltd. wishes to maintain enough safety
stock during the lead time period between
starting a new production run and its completion
such that the probability of satisfying the
customer demand during the lead time period
is 95\%. The lead time periods is 5 days and
daily customer demand can be assumed to follow
the Gaussian (normal) distribution with mean
50 units and a standard deviation of 10 units.
Using $\phi^{-1}$(0.95) =1.64 , where $\phi$ represents the
cumulative distribution function of the standard
normal random variable, the amount of safety
stock that must be maintained by Robot Ltd. to
achieve this demand fulfillment probability for
the lead time period is \rule{1cm}{0.15mm}  units (round off to
two decimal places).
%
\solution
  \input{solutions/adv/me/2021/20.tex}
  

\end{enumerate}