\renewcommand{\theequation}{\theenumi}
\renewcommand{\thefigure}{\theenumi}
\renewcommand{\thetable}{\theenumi}
\begin{enumerate}[label=\thesection.\arabic*.,ref=\thesection.\theenumi]
\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}
\numberwithin{table}{enumi}

\item A fair coin is tossed till a head appears for the first time. The probability that the number of requried tosses is odd,is
\begin{enumerate}
\begin{multicols}{4}
\setlength\itemsep{2em}
\item $
\dfrac{1}{3}
$
\item $
\dfrac{1}{2}
$
\item $
\dfrac{2}{3}
$
\item $
\dfrac{3}{4}
$
\end{multicols}
\end{enumerate}
\solution
\input{solutions/ec/25.tex}

%
\item A fair coin is tossed till a head appears for the first time. The probability that the number of requried tosses is odd,is
\begin{enumerate}
\begin{multicols}{4}
\setlength\itemsep{2em}
\item $
\dfrac{1}{3}
$
\item $
\dfrac{1}{2}
$
\item $
\dfrac{2}{3}
$
\item $
\dfrac{3}{4}
$
\end{multicols}
\end{enumerate}
%
\solution
\input{markov/solutions/1.tex}

%



\item \textbf{Step 1.} Flip a coin twice.\\
\textbf{Step 2.} If the outcomes are (TAILS, HEADS) then output Y and stop.\\
\textbf{Step 3.} If the outcomes are either (HEADS, HEADS) or (HEADS, TAILS), then output N and stop.\\
\textbf{Step 4.} If the outcomes are (TAILS, TAILS), then go to Step 1.\\
The probability that the output of the experiment is Y is (upto two decimal places)......
\\
%
\solution
\input{solutions/ec/9.tex}

%
\item Players A and B take turns to throw a fair dice with six faces. If A is the first player to throw, then the probability of B being the first one to get a six is --- ( round of to two decimal places). \\
\solution
\input{solutions/xe/2020/11.tex}
%
\item A fair coin is tossed till a head appears for the first time. The probability that the number of requried tosses is odd,is\\
\begin{enumerate}
    \item $\dfrac{1}{3}$\\
    \item $\dfrac{1}{2}$\\
    \item $\dfrac{2}{3}$\\
    \item $\dfrac{3}{4}$
\end{enumerate}
\solution
  \input{solutions/adv/ec/25.tex}
%
\item  Consider the experiment with the following steps.
\begin{enumerate}
\item  Flip a coin twice.
\item If the outcomes are (TAILS, HEADS) then output Y and stop.
\item If the outcomes are either (HEADS, HEADS) or (HEADS, TAILS), then output N and stop.
\item If the outcomes are (TAILS, TAILS), then go to Step 1.
\end{enumerate}
The probability that the output of the experiment is Y is (upto two decimal places)......
\\
\solution 
  \input{solutions/adv/cs/2016/29.tex}
  Consider a simple symmetric random walk on integers, where from every state i you move to i-1 and i+1 with the probability half each. Then which of the following are true?
  \begin{enumerate}
  \item The random walk is aperiodic
  \item The random walk is irreducible
  \item The random walk is null recurrent 
  \item The random walk is positive recurrent
  \end{enumerate}

\end{enumerate}