\renewcommand{\theequation}{\theenumi}
\renewcommand{\thefigure}{\theenumi}
\renewcommand{\thetable}{\theenumi}
\begin{enumerate}[label=\thesection.\arabic*.,ref=\thesection.\theenumi]
\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}
\numberwithin{table}{enumi}


\item Let $X_n$ denote the sum of points obtained when n fair dice are rolled together. The expectation and variance of $X_n$ are

\begin{enumerate}
\begin{multicols}{2}
\setlength\itemsep{1em}
{\scriptsize
\item ${\dfrac{7}{2}}n$ and ${\dfrac{35}{12}}n^2$ respectively.
\item ${\dfrac{7}{2}}n$ and ${\dfrac{35}{12}}n$ respectively.
\item $ \bigg (\dfrac{7}{2} \bigg )^n$ and $ \bigg (\dfrac{35}{12} \bigg )^n$ respectively.
\item None of the above
}
\end{multicols}
\end{enumerate}
\solution
\input{solutions/ec/64.tex}

%
\item
Consider that X and Y are independent continuous valued random variables with uniform PDF given by $X\sim U(2,3)$ and $Y\sim U(1,4)$. Then $\pr{Y\le X}$ is equal to .....
\\
\solution
\input{solutions/in/2021/main.tex}
%

%
\item Given Set A = \{2,3,4,5\} and Set B = \{11,12,13,14,15\}, two numbers are randomly selected, one from each set. What is probability that the sum of the two numbers equals 16?
\\
%
\solution
\input{solutions/ee/2015/2/Assignment5.tex}

%
\item Let X and Y be two statistically independent random variables uniformly distributed in the range (-1, 1) and (-2, 1) respectively. Let $Z = X +Y$ , then the probability that $[Z \leq -2]$ is\\
(A) 0\\
(B) $\frac{1}{6}$\\
(C) $\frac{1}{3}$\\
(D) $\frac{1}{12}$
%\\
%\solution
%\input{solutions/ec/2003/61/Assignment_4.tex}

%
\item Two die are thrown. What is the probability that sum of numbers on the two dice is eight \\
\begin{enumerate}[label=(\alph*)]
\item $\frac{5}{36}$\\
\item $\frac{5}{18}$ \\
\item$\frac{1}{4}$\\
\item$\frac{1}{3}$
\end{enumerate}
%
%
\solution
\input{solutions/me/2002/1.1.tex}

\item Four fair six-sided dice are rolled.The probability that sum of results being 22 is $\frac{X}{1296}$.the value of X is
%
\solution
\input{solutions/cs/2014/48/assignment4.tex}

%
\item Let $X$ and $Y$ be two statistically independent random variables uniformly
distributed in the ranges $(-1,1)$ and $(-2,1)$ respectively. Let $Z = X + Y.$ then the probability that $[Z\leq-2]$ is
\begin{enumerate}[label=\alph*)]
\item zero
\item $\frac{1}{6}$
\item $\frac{1}{3}$
\item $\frac{1}{12}$
\end{enumerate}
%
\solution
\input{solutions/ec/2003/61.tex}

%
\item A single die is thrown twice. What is the probability that the sum is neither 8 or 9?
    \begin{enumerate}[label=(\alph*)]
        \item \large$\frac{1}{9}$
        \item \large$\frac{5}{36}$
        \item \large$\frac{1}{4}$
        \item \large$\frac{3}{4}$
    \end{enumerate}
%
\solution
\input{solutions/me/2005/38.tex}
%

\end{enumerate}