\renewcommand{\theequation}{\theenumi}
\renewcommand{\thefigure}{\theenumi}
\renewcommand{\thetable}{\theenumi}
\begin{enumerate}[label=\thesection.\arabic*.,ref=\thesection.\theenumi]
\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}
\numberwithin{table}{enumi}


\item In the following table, $X$ is a discrete random variable and $p(X=x)$ is the probability density. The standard deviation of $X$ is 
%
\begin{table}[h!]
    \centering
    \begin{tabular}{|c|c|c|c|}
        \hline
        $X$ & 1 & 2 & 3  \\
        \hline
        $p_X(k)$ & 0.3 & 0.6 & 0.1\\
        \hline
    \end{tabular}
    \label{cond/1/tab:my_label}
    \caption{Probability Distribution}
\end{table}
\\
\solution
\input{cond/solutions/1.tex}
%
\item An urn contains 5 red balls and 5 black balls.In the first draw, one ball is picked at random and discarded without noticing its colour.The probability to get a red ball in the second draw is

\begin{enumerate}
\begin{multicols}{4}
\setlength\itemsep{2em}

\item $\dfrac{1}{2}$
\item $\dfrac{4}{9}$
\item $\dfrac{5}{9}$
\item $\dfrac{6}{9}$
\end{multicols}
\end{enumerate}
\solution
\input{solutions/1/1.tex}
%
\item Out of all the 2-digit integers between 1 and 100, a 2-digit number has to be selected at random. What is the probability that the selected number is not divisible by 7?
\begin{enumerate}[label = (\Alph*)]
\item $\frac{13}{90}$\\
\item $\frac{12}{90}$\\
\item $\frac{78}{90}$\\
\item $\frac{77}{90}$
\end{enumerate}
%
\solution
\input{cond/solutions/2.tex}
%



\item There are 3 red socks, 4 green socks and 3 blue socks.You choose 2 socks.The probability that they are of the same colour is

\begin{enumerate}
\begin{multicols}{4}
\setlength\itemsep{2em}

\item $\dfrac{1}{5}$
\item $\dfrac{7}{30}$
\item $\dfrac{1}{4}$
\item $\dfrac{4}{15}$

\end{multicols}
\end{enumerate}
\solution
\input{solutions/ec/2.tex}

\item The probability that a \textit{k}-digit number does NOT contain the digits 0,5, or 9 is

\begin{enumerate}
\begin{multicols}{4}
\setlength\itemsep{2em}

\item $0.3^k$
\item $0.6^k$
\item $0.7^k$
\item $0.9^k$

\end{multicols}
\end{enumerate}
\solution
\input{solutions/3.tex}
%
\item Candidates were asked to come to an interview with 3 pens each. Black,blue,green and red were the permitted pen colours that the candidate could bring. The probability that a candidate comes with all 3 pens having the same colour is.......
%
\item Let X and Y denote the sets containing 2 and 20 distinct objects respectively and F denote the set of all possible functions defined from X and Y. Let f be randomly chosen from F. The probability of f being one-to-one is........
%
\item Consider a dice with the property that the probability of a face with \textit{n} dots showing up is proportional to \textit{n}. The probability of the face with three dots showing up is......
%
\solution
\input{solutions/ec/8.tex}

\item A box contains 4 white balls and 3 red balls. In succession, two balls are randomly selected and removed from the box. Given that the first removed ball is white, the probability that the second removed ball is red is
\begin{enumerate}
\begin{multicols}{4}
\setlength\itemsep{2em}
\item $
\dfrac{1}{3}
$
\item $
\dfrac{3}{7}
$
\item $
\dfrac{1}{2}
$
\item $
\dfrac{4}{7}
$

\end{multicols}
\end{enumerate}
\solution
\input{solutions/19/19.tex}
%
\item A discrete random variable X takes values from 1 to 5 with probabilities as shown in the table. A student calculates the mean of X as 3.5 and her teacher calculates the variance of X as 1.5. Which of the following statements is true?

\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}\hline

k & 1 & 2 & 3 & 4 & 5\\ \hline
P(X=k) & 0.1 & 0.2 & 0.4 & 0.2 & 0.1\\ \hline
\end{tabular}
\end{center}

\begin{enumerate}
\item Both the student and the teacher are right
\item Both the student and the teacher are wrong
\item The student is wrong but the teacher is right
\item The student is right but the teacher is wrong
\end{enumerate}
%
\item If E denotes expectation, the variance of a random variable X is given by
\begin{enumerate}
\begin{multicols}{2}
\setlength\itemsep{2em}
\item $
E[X^2]-E^2[X]
$
\item $
E[X^2]+E^2[X]
$
\item $
E[X^2]
$
\item $
E^2[X]
$
\end{multicols}
\end{enumerate}
%
\solution
\input{solutions/ec/30.tex}
%
\item An examination consists of two papers, Paper 1 and Paper 2. The probability of failing in Paper 1 is 0.3 and that in Paper 2 is 0.2. Given that a student has failed in Paper 2, the probability of failing in Paper 1 is 0.6. The probability  of a student failing in both the papers is:
\begin{enumerate}
\begin{multicols}{4}
\setlength\itemsep{2em}
\item 0.5
\item 0.18
\item 0.12
\item 0.06

\end{multicols}
\end{enumerate}
%
\solution
\input{solutions/ec/31.tex}
%
\item Let U and V be two independent and identically distributed random variables such that $
P(U=+1)=P(U=-1)=\dfrac{1}{2}.
$
The entropy H(U+V) in bits is

\begin{enumerate}
\begin{multicols}{4}
\setlength\itemsep{2em}
\item $
\dfrac{3}{4}
$
\item 1
\item $
\dfrac{3}{2}
$
\item $\log_23
$

\end{multicols}
\end{enumerate}

\item Let $(X_1,X_2)$ be independent random variables. $X_1$ has mean 0 and variance 1, while $X_2$ has mean 1 and variance 4. The mutual information I $(X_1;X_2)$ between $X_1$ and $X_2$ in bits is.......

\item A binary communication system makes use of the symbols "zero" and "one". There are channel errors. Consider the following events:
\begin{itemize}
\item $x_0$:a "zero" is transmitted
\item $x_1$:a "one" is transmitted
\item $y_0$:a "zero" is received
\item $y_1$:a "one" is received
\end{itemize}
%
The following probabilities are given: $P(x_0) = \frac{1}{2}$, $P(y_0|x_0)= \frac{3}{4}$, and $P(y_0|x_1)= \frac{1}{2}$. The information in bits that you obtain when you learn which symbol has been received (while you know that a "zero" has been transmitted) is .........

\item Consider two identical boxes $B_1$ and $B_2$, where the box $B(i=1,2)$ contains $i+2$ red and $5-i-1$ white balls. A fair die is cast. Let the number of dots shown on the top face of the die be N. If N is even or 5, then two balls are drawn with replacement from the box $B_1$, otherwise, two balls are drawn with replacement from the box $B_2$. The probability that the two drawn balls are of different colours is

\begin{enumerate}
\begin{multicols}{2}
\setlength\itemsep{2em}

\item $\dfrac{7}{25}$
\item $\dfrac{9}{25}$
\item $\dfrac{12}{25}$
\item $\dfrac{16}{25}$

\end{multicols}
\end{enumerate}
\solution
\input{solutions/ec/66.tex}

\item You have gone to a cyber-cafe with a friend. You found that the cyber-café has only three terminals. All terminals are unoccupied. You and your friend have to make a random choice of selecting a terminal. What is the probability that both of you will NOT select the same terminal?
%
\\
\solution
\input{solutions/in/2006.tex}

\item What is the chance that a leap year,selected at random,will contain 53 Saturdays? \\
\begin{enumerate}
    \item  $\frac{2}{7}$ 
    \item  $\frac{3}{7}$ 
    \item  $\frac{1}{7}$ 
    \item  $\frac{5}{7}$ 
\end{enumerate}
\solution
\input{solutions/ee/2013.tex}

\item Let $\mathcal{R}$  be the set of all binary relations on the set $\{1,2,3\}$. Suppose a relation is chosen from $\mathcal{R}$ at random. The probability that the chosen relation is reflexive is?
\\
\solution
\input{solutions/cs/2020.tex}

\item Box-S has $2$ white and $4$ black balls and box-T has $5$ white and $3$ black balls.A ball is drawn at \\ random from box-S and put in box-T.Subsequently,the probability of drawing a white ball from box-T is? (rounding off to $ 2 $ decimal places)
%
\\
\solution
\input{solutions/xe/2017/17.tex}
%
\item A box contains 4 white balls and 3 red balls. In succession, two balls are randomly selected and removed from the box. Given that the first removed ball is white, the probability that the second removed ball is red is 
%
\\
\solution
\input{solutions/ee/2010/27.tex}
\item Two dice are thrown simultaneously. The probability that the product of the numbers appearing on the top faces of the dice is a perfect square is  \\ \\
(A)$\dfrac{1}{9}$         \hfill  (B) $\dfrac{2}{9}$  \hfill
(C)$\dfrac{1}{3}$      \hfill       (D)$\dfrac{4}{9}$  
\\
\solution
\input{solutions/xe/2017/170.tex}

\item What is the chance that a leap year,selected at random,will contain 53 Saturdays? \\
\begin{enumerate}
    \item  $\frac{2}{7}$ 
    \item  $\frac{3}{7}$ 
    \item  $\frac{1}{7}$ 
    \item  $\frac{5}{7}$ 
\end{enumerate}
%
\solution
\input{solutions/ee/2013/61.tex}

%
\item An automobile plant contracted to buy shock absorbers from two suppliers $X$ and $Y . X$ supplies $60 \%$ and $Y$ supplies $40 \%$ of the shock absorbers. All shock absorbers are subjected to a quality test. The ones that pass the quality test are considered reliable. Of X's shock absorbers, $96 \%$ are reliable. Of Y's shock absorbers, $72 \%$ are reliable.
The probability that a randomly chosen shock absorber, which is found to be reliable, is made by $Y$ is
\begin{enumerate}
\item  0.288
\item 0.334
\item  0.667
\item 0.720
\end{enumerate}
%
\solution
\input{solutions/cs/2012/63/exercise_4_main_tex.tex}

%
\item A person who speaks truth $3$ out of $4$ times,throws a fair dice with six faces and informs the outcome is $5$.The probability that the outcome is really $5$ is
\\
\solution
\input{solutions/xe/2021/9.tex}

%
\item  The probabilities that a student passes in Mathematics, Physics and Chemistry are m,p, and
c respectively. Of these subjects, the student has 75\% chance of passing in at least one, a
50\% chance of passing in at least two and a 40\% chance of passing in exactly two.
Following relations are drawn in m, p, c:
    \begin{enumerate}[label=(\Roman*)]
        \item p + m + c = 27/20
        \item p + m + c = 13/20
        \item (p)$\times$ (m) $\times$ (c) =1/10
    \end{enumerate}
    \begin{enumerate}[label=(\Alph*)]
      \item Only relation I is true
      \item Only relation II is true
      \item Relations II and III are true
      \item Relations I and III are true
    \end{enumerate}
%
\solution
\input{solutions/ee/2015/10.tex}

%
\item Let $X$ and $Y$ denote the sets consisting 2 and 20 distinct elements respectively and $F$ denote the set of all possible functions defined from $X$ and $Y$. Let $f$ be randomly chosen from $F$. The probability of f being one to one is :
\\
\solution
\input{solutions/cs/2015/54.tex}

%
\item The probability that a number selected at random between 100 and 999 (both inclusive) will not contain digit 7 is.
\solution
\input{solutions/cs/1995/18.tex}

%
\item A class of twelve children has two more boys than girls. A group of three children are randomly picked from this class to accompany the teacher on the field trip. What is the probability that the group accompanying the teacher contains more girls than boys.\\
\begin{enumerate}[label=(\alph*)]
\item $0$\\
\item $\frac{325}{864}$ \\
\item$\frac{525}{864}$\\
\item$\frac{5}{12}$
\end{enumerate}
\solution
\input{solutions/ee/2018/8.tex}

%
\item Suppose that a shop has an equal number of LED bulbs of two different types. The probability of an LED bulb lasting more than 100 hours given that it is of Type 1 is 0.7, and given that it is of Type 2 is 0.4. The probability that an LED bulb chosen uniformly at random lasts more than 100 hours is
\\
\solution 
\input{solutions/cs/2016/5.tex}

%
\item The probability that a given positive integer lying between 1 and 100 ( both inclusive) and is NOT divisible by 2 or 3 or 5 is \dots
\\
\solution
\input{solutions/cs/2014/48-1.tex}

%
\item What is the probability that a divisor of $10^{99}$ is a multiple of $10^{96}$ ?
\vspace{0.5 cm}
(A) $\dfrac{1}{625}$ \hspace{0.5 cm} (B) $\dfrac{4}{625}$ \hspace{0.5 cm} (C) $\dfrac{12}{625}$ \hspace{0.5 cm} (D) $\dfrac{16}{625}$
%
\\
\solution
\input{solutions/cs/2010/27.tex}

%
\item There are five bags each containing identical sets of ten distinct chocolates. One chocolate is picked from each bag.\\
The probability that atleast two chocolates are identical is?\\
\solution
\input{solutions/cs/2021/8.tex}

%
\item Raju has four fair coins and one fair dice. At first Raju tosses a coin. If the coin shows head then he rolls the dice and the number that dice shows is taken as his score. If the coin shows tail then he tosses three more coins and the total number of tails shown (including the first one) is taken as his score. If Raju tells that his score is 2 then the probability that he rolled the dice is (up to two decimal places):
%
\\
\solution
\input{solutions/ec/29-1/Assignment3.tex}

%
\item A bag contains 10 white balls and 15 black balls . Two balls are drawn in succession. The probability that one of them is white and the other is black is.
\\
\solution
\input{solutions/cs/1995/39.tex}

%
\item The box 1 contains chips numbered 3, 6, 9, 12 and 15. The box 2 contains chips numbered 6, 11, 16, 21 and 26.
Two chips, one from each box are drawn at random. The numbers written on these chips are multiplied. The probability 
for the product to be an even number is
%
\begin{enumerate}
\item $\frac{6}{25}$
\item $\frac{2}{5}$
\item $\frac{3}{5}$
\item $\frac{19}{25}$
\end{enumerate}
%
\solution
\input{solutions/in/2011/28.tex}
%
\item A box contains 25 parts of which 10 are defective. Two parts are being drawn simultaenously in a random manner from the box. The probability of both parts being good is\\
$(A)\frac{7}{20}\ \ \ (B)\frac{42}{125}\ \ \ (C)\frac{25}{29}\ \ \ (D)\frac{5}{9}$
%
\solution
\input{solutions/me/2014/4.tex}
%
\item From a pack of regular playing cards, two cards are drawn at random. What is
the probability that both cards will be Kings, if the first card is NOT replaced?
    \begin{enumerate}
    \item $\frac{1}{26}$
    \item $\frac{1}{52}$
    \item $\frac{1}{169}$
    \item $\frac{1}{221}$
\end{enumerate}
%
\solution
\input{solutions/me/2004/32.tex}
%
\item A group consists of equal number of men and women. Of this group, 20\% of the men and 50\% of the women are unemployed. If a person is selected at random from this group, the probability of the selected person being employed is  
%
\solution
\input{solutions/me/2014/4-1.tex}
%

%
\item The probability that a student knows the correct answer to a multiple choice question is $\frac{2}{3}$. If the student does not know the answer, then the student guesses the answer. The probability of the guessed answer being correct is $\frac{1}{4}$. Given that the student has answered the question correctly, the conditional probability that the student knows the correct answer is

    \begin{enumerate}
        \item $\frac{2}{3}$
        \item $\frac{3}{4}$
        \item $\frac{5}{6}$
        \item $\frac{8}{9}$
    \end{enumerate}
%
\solution
\input{solutions/me/2013/45.tex}
%
\item Consider an unbiased cubic dice with opposite faces coloured identically and each face coloured red, blue or green such that each colour appears only two times on the dice. If the dice is thrown thrice, the probability of obtaining red colour on top face of the dice at least twice is $\rule{1.6cm}{0.15mm}$ .
%
\solution
\input{solutions/me/2014/28.tex}


\item  The chance of a student passing an exam is 20\%. The chance of a student passing the exam and getting above 90\% marks is 5\%. GIVEN that a student passes the examination, the probability that the student gets above 90\% marks is
%
\\
\solution
\input{solutions/me/2015/26.tex}

\item Four red balls, four green balls and four blue balls are put in a box. Three balls are pulled out of the box at random one after another without replacement. The probability that all the three balls are red is  
%
\\
\solution
\input{solutions/me/2018/1.tex}
%
\item Consider a company that assembles computers.The probability of a faulty assembly of any computer is p.The company therefore subjects each computer to testing process.This testing process gives the correct result for any computer with a probability of q.What is the probability of a computer being declared faulty?
\begin{enumerate}
\item pq+(1-p)(1-q)
\item (1-q)p
\item (1-p)q
\item pq
\end{enumerate}
%
\solution
\input{solutions/cs/2010/26.tex}

%
\item  An array of 25 distinct elements is to be sorted using quicksort. Assume that the pivot element is chosen uniformly at random. The probability that the pivot element gets placed in the worst possible location in the first round of partitioning (rounded off to 2 decimal places) is ----
%
\solution
\input{solutions/cs/2019/20.tex}

%
\item  There are 3 red socks, 4 green socks and 3 blue socks. You choose 2 socks. The probability that they are of the same colour is 

\begin{enumerate}
    \item $\frac{1}{5}$
    \item $\frac{7}{30}$
    \item $\frac{1}{4}$ 
    \item $\frac{4}{15}$ 
\end{enumerate}
%
\solution
\input{solutions/cs/2017/60.tex}

%
\item Suppose we uniformly and randomly select a permutation from the 20\(!\) permutations of 1,2,3,\ldots,20. What is the probability that 2 appears at an earlier position than any other even number in the selected permutation.
\begin{enumerate}[label=(\Alph*)]
    \item \(\displaystyle\frac{1}{2}\)\newline
    \item \(\displaystyle\frac{1}{10}\)\newline
    \item \(\displaystyle\frac{9!}{20!}\)\newline
    \item \normalsize{None of the above.}\newline
\end{enumerate}

%
\solution
\input{solutions/cs/1996/5.tex}

\item Aishwarya studies either computer science or mathematics everyday. If she studies computer science on a day, then the probability she studies mathematics the next day is 0.6. If she studies mathematics on a day, then the probability she studies computer science the next day is 0.4.
Given that Aishwarya studies computer science on Monday, what is the probablity she studies computer science on Wednesday?
\begin{enumerate}[label=(\Alph*)]

%\setlength\itemsep{2em}
\item 0.24
\item 0.36
\item 0.4
\item 0.6

\end{enumerate}
%
\solution
\input{solutions/cs/2008/27.tex}

%
\item  The probability that the top and bottom cards of a randomly shuffled deck are both aces is
\begin{description}
\item[$\brak{A}$]$\dfrac{4}{52}\times\dfrac{4}{52}$ \\
\item[$\brak{B}$]$\dfrac{4}{52}\times\dfrac{3}{52}$ \\
\item[$\brak{C}$]$\dfrac{4}{52}\times\dfrac{3}{51}$ \\
\item[$\brak{D}$]$\dfrac{4}{52}\times\dfrac{4}{51}$ \\
\end{description}
%
\solution
\input{solutions/cs/1996/32.tex}

%
\item Suppose a fair six-sided die is rolled once. If the value on the die is 1,2, or 3, the die is rolled a second time. What is the probability that the sum total of values that turn up is at least 6?
\begin{enumerate}
    \item 10/21
    \item 5/12
    \item 2/3
    \item 1/6
\end{enumerate}
%
\solution
\input{solutions/cs/2012/33.tex}

%
\item A box contains 4 red balls and 6 black balls. Three balls are selected randomly from the box one after another, 
without replacement. What is the probability that the selected set contains one red ball and two black balls?\bigskip
\begin{enumerate}\itemsep0.3cm
    \item $\displaystyle{\frac{1}{20}}$
    \item $\displaystyle{\frac{1}{12}}$
    \item $\displaystyle{\frac{3}{10}}$
    \item $\displaystyle{\frac{1}{2}}$
\end{enumerate}
%
\solution
\input{solutions/me/2012/45.tex}

\item A box contains 2 washers, 3 nuts and 4 bolts. Items are drawn from the box at random one at a time without replacement. The probability of drawing 2 washers first followed by 3 nuts and subsequently 4 bolts is
%
    \begin{enumerate}[label=(\Alph*)]
        \item \large$\frac{2}{315}$
        \item \large$\frac{1}{630}$
        \item \large$\frac{1}{1260}$
        \item \large$\frac{1}{2520}$
    \end{enumerate}
%
%
\solution
\input{solutions/me/2010/30.tex}

%
\item A box contains 15 blue balls and 45 black balls. If two balls are selected randomly, without replacement, the probability of an outcome in which the first ball selected is a blue ball and the second ball selected is a black ball, is .....

    \begin{enumerate}[label=\arabic*.]
        \item \Large$\frac{3}{16}$ \\
        \item $\frac{45}{236}$
        \item $\frac{1}{4}$ \\
        \item $\frac{3}{4}$
    \end{enumerate}
%
\solution
\input{solutions/me/2021/7.tex}

%
\item An automobile plant contracted to buy shock absorbers from two suppliers X and Y. X supplies 60\% and y supplies 40\% of the shock absorbers. All shock absorbers are subjected to a quality test.The ones that pass the quality test are considered reliable. Of X's shock absorbers are 96\% are reliable. Of Y's shock absorbers 72\% are reliable The probability that a randomly chosen shock absorber which is found to be reliable is made by Y is
\begin{enumerate}
    \item 0.288
    \item 0.334
    \item 0.667
    \item 0.720
\end{enumerate}
%
\solution
\input{solutions/me/2012/64.tex}

%
\item There are two identical locks, with two identical keys, and the keys are among the six different ones which a person carries in his pocket. In a hurry he drops one key somewhere. Then the probability that the locks can still be opened by drawing one key at random is equal to?
%
\solution
\input{solutions/ma/2002/2.23.tex}



\end{enumerate}